%==============================================================================
%  Valter Nunez — CV  ·  DATA SCIENCE variant (1 page, ATS-friendly)
%  Leads with quantitative foundation + DS projects; backend reframed as
%  data-intensive systems work. Compile: XeLaTeX (Overleaf) or `tectonic`.
%==============================================================================
\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}
\renewcommand*\familydefault{\sfdefault}
\usepackage[margin=1.15cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}

\definecolor{ink}{HTML}{0A0A0A}
\definecolor{accent}{HTML}{2563EB}
\definecolor{soft}{HTML}{45474B}
\color{ink}
\hypersetup{colorlinks=true, urlcolor=accent}

\setlength{\parindent}{0pt}
\linespread{1.04}
\pagestyle{empty}

\titleformat{\section}
  {\large\bfseries\color{ink}}{}{0em}{}
  [\vspace{-0.55em}\color{accent}\rule{\linewidth}{1.1pt}]
\titlespacing*{\section}{0pt}{0.65em}{0.45em}

\newcommand{\role}[4]{%
  \textbf{#1} \hfill \textbf{#3}\\[1pt]
  {\color{soft}\textit{#2} \hfill \textit{#4}}\par\vspace{2pt}}
\newcommand{\project}[2]{\textbf{#1} \,---\, #2\par\vspace{1pt}}
\newcommand{\skill}[2]{\textbf{\color{soft}#1:}\ #2\par\vspace{1.5pt}}

\newlist{tight}{itemize}{1}
\setlist[tight]{leftmargin=1.1em, itemsep=1.6pt, topsep=2pt, parsep=0pt,
  label=\textcolor{accent}{\small$\bullet$}}

\begin{document}

{\Huge\bfseries Valter Nunez}\\[3pt]
{\color{soft}\large Software Engineer $\rightarrow$ Data Science \;\textbar\; MSc Data Science, LSE (London)}\\[5pt]
{\small
\href{mailto:valter.nunez@outlook.com}{valter.nunez@outlook.com} \quad\textcolor{soft}{|}\quad
\href{https://www.linkedin.com/in/valternunez}{linkedin.com/in/valternunez} \quad\textcolor{soft}{|}\quad
\href{https://valternunez.github.io}{valternunez.github.io}
}

\section*{Summary}
Software engineer moving into data science: a solid quantitative foundation (calculus,
linear algebra, probability) and self-driven projects in \textbf{Bayesian inference} and
natural-experiment design. Five years building data-intensive, event-driven backends for high-traffic
e-commerce: schemas, telemetry, analytics pipelines. Now studying \textbf{MSc Data Science at LSE} in
London (UK Graduate visa, 18 months, no sponsorship required); seeking Skilled Worker sponsorship to stay long-term.

\section*{Data Science Projects}
\begin{tight}
  \item \project{Ballon d'Or attention study}{Bayesian two-stage (nomination/placement) decomposition in \textbf{PyMC} over \textasciitilde210 player-seasons, isolating an unexplained media-attention residual after controlling for merit and team success; media pull on nomination is \textasciitilde5$\times$ its pull on placement, robust across placebo and regression-to-the-mean checks. Ships as a D3 scrollytelling site + Quarto report.}
  \item \project{World Cup 2026 momentum}{treats the tournament's mandatory hydration breaks as a natural experiment, using duration-matched stoppage comparisons + placebo tests; a pipeline (local scrape $\rightarrow$ GitHub Actions $\rightarrow$ Pages) regenerated the report daily.}
  \item \project{Insurance-claims regression}{implemented linear regression from scratch (variance, covariance, coefficients) and with scikit-learn, evaluated by RMSE on held-out Swedish auto-insurance data.}
\end{tight}

\section*{Experience}
\role{Backend Engineer}{ZeBrands — high-traffic e-commerce}{Sep 2021 -- Mar 2026}{Remote, Mexico}
\begin{tight}
  \item Co-architected and built \textbf{OZ}, an event-driven platform that sustains sales through ERP outages, decoupling 83\% of revenue-critical sales flows from synchronous ERP calls; designed the schemas and telemetry behind its reliability analytics (FastAPI, PostgreSQL, RabbitMQ, Redis); now live across \textit{\textasciitilde195 stores} (Mexico, expanding to Brazil), sustaining \textit{\textasciitilde MX\$102M} over the nine-day Hot Sale peak.
  \item Co-designed and built multi-carrier shipping middleware with automated least-cost routing, cutting total shipping spend \textasciitilde78\%; migrated review analytics into a dedicated service for client-side insights.
  \item Maintained existing client-facing microservices and GraphQL data APIs (Frappe, TypeScript); stood up Grafana logging/observability (issue detection, performance dashboards).
\end{tight}
\vspace{3pt}
\role{Co-Founder \& Developer}{Laiter — software studio}{2017 -- 2019}{Mexico}
\begin{tight}
  \item Built Django web apps and the early usage-analytics dashboards clients ran decisions on.
\end{tight}

\section*{Education}
\role{MSc Data Science}{London School of Economics (LSE)}{2026 -- 2027}{In progress, London}
\vspace{2pt}
\role{B.S. Computer Science \& Technology}{Tecnológico de Monterrey (ITESM)}{2016 -- 2021}{Avg 90/100}
\vspace{1pt}
{\color{soft}\small Quantitative coursework: Calculus I--III, Linear Algebra, Probability \& Statistics, Numerical Methods, Simulation. Semester abroad at RMIT Melbourne (Avg 94/100). IBM Data Science Professional Certificate (in progress).}

\section*{Technical Skills}
\skill{Data Science}{Python, pandas, NumPy, scikit-learn, PyMC, Bayesian inference, statistics, matplotlib/D3, Quarto}
\skill{AI / LLM}{LLM integration (Gemini) with metering \& structured output; agent-orchestrated development}
\skill{Data \& Databases}{SQL, PostgreSQL, Redis, MongoDB, RabbitMQ}
\skill{Engineering}{FastAPI, Django, TypeScript, Docker, Git, GitHub Actions}
\skill{Languages spoken}{Spanish (Native), English (C2), German (A2), Italian (A1)}

\end{document}
