%==============================================================================
%  Valter Nunez — CV  ·  FOUNDING / FULL-STACK ENGINEER variant (1 page)
%  Leads with end-to-end ownership: solo-built Nexus + co-founded Laiter.
%  Compile: XeLaTeX (Overleaf) or `tectonic`.
%==============================================================================
\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}
\renewcommand*\familydefault{\sfdefault}
\usepackage[margin=1.15cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}

\definecolor{ink}{HTML}{0A0A0A}
\definecolor{accent}{HTML}{2563EB}
\definecolor{soft}{HTML}{45474B}
\color{ink}
\hypersetup{colorlinks=true, urlcolor=accent}

\setlength{\parindent}{0pt}
\linespread{1.04}
\pagestyle{empty}

\titleformat{\section}
  {\large\bfseries\color{ink}}{}{0em}{}
  [\vspace{-0.55em}\color{accent}\rule{\linewidth}{1.1pt}]
\titlespacing*{\section}{0pt}{0.65em}{0.45em}

\newcommand{\role}[4]{%
  \textbf{#1} \hfill \textbf{#3}\\[1pt]
  {\color{soft}\textit{#2} \hfill \textit{#4}}\par\vspace{2pt}}
\newcommand{\project}[2]{\textbf{#1} \,---\, #2\par\vspace{1pt}}
\newcommand{\skill}[2]{\textbf{\color{soft}#1:}\ #2\par\vspace{1.5pt}}

\newlist{tight}{itemize}{1}
\setlist[tight]{leftmargin=1.1em, itemsep=1.6pt, topsep=2pt, parsep=0pt,
  label=\textcolor{accent}{\small$\bullet$}}

\begin{document}

{\Huge\bfseries Valter Nunez}\\[3pt]
{\color{soft}\large Founding / Full-stack Engineer}\\[5pt]
{\small
\href{mailto:valter.nunez@outlook.com}{valter.nunez@outlook.com} \quad\textcolor{soft}{|}\quad
\href{https://www.linkedin.com/in/valternunez}{linkedin.com/in/valternunez} \quad\textcolor{soft}{|}\quad
\href{https://valternunez.github.io}{valternunez.github.io}
}

\section*{Summary}
Engineer who ships whole products: backend, frontend, payments, infrastructure.
Solo-architected \textbf{Nexus}, a multi-tenant SaaS with a double-entry finance engine and Stripe
Connect, built with an orchestrated multi-agent dev workflow (AI coding agents + git worktrees).
Co-founded a software studio. Five years on high-traffic e-commerce building event-driven systems
with measured impact (decoupled 83\% of sales flows from the ERP; cut shipping spend
\textasciitilde78\%). Now studying \textbf{MSc Data Science, LSE} in London (UK Graduate visa, 18
months, no sponsorship required); seeking Skilled Worker sponsorship to stay long-term.

\section*{Selected Projects}
\begin{tight}
  \item \project{Nexus (solo)}{multi-tenant SaaS for property administration, architected and built end to end: double-entry \textbf{finance engine} (ledgers, billing, payouts), \textbf{Stripe Connect} (charges, SPEI, disputes, reconciliation), per-tenant RBAC, async pipeline (Celery/RabbitMQ), an LLM assist (Gemini) with metering \& structured output, and a Next.js 16 PWA frontend. Shipped solo via an orchestrated multi-agent dev workflow (specialist implement/review/audit agents, git worktrees).}
  \item \project{Ballon d'Or attention study}{Bayesian decomposition (PyMC) shipped as a D3 scrollytelling site + Quarto report, an end-to-end data product.}
  \item \project{World Cup 2026 momentum}{natural-experiment pipeline (local scrape $\rightarrow$ GitHub Actions $\rightarrow$ Pages) that regenerated daily.}
\end{tight}

\section*{Experience}
\role{Backend Engineer}{ZeBrands — high-traffic e-commerce}{Sep 2021 -- Mar 2026}{Remote, Mexico}
\begin{tight}
  \item Co-architected and built \textbf{OZ}, an event-driven resilience platform (FastAPI, PostgreSQL, RabbitMQ, Redis), decoupling 83\% of revenue-critical sales flows from the ERP; projected a 91\% reduction in sales-blocking downtime; now live across \textit{\textasciitilde195 stores} (Mexico, expanding to Brazil), sustaining \textit{\textasciitilde MX\$102M} over the nine-day Hot Sale peak.
  \item Co-designed and built multi-carrier shipping middleware with automated least-cost routing (\textasciitilde78\% lower shipping spend); maintained existing client-facing microservices, GraphQL APIs, and Grafana observability; mentored a junior developer.
\end{tight}
\vspace{3pt}
\role{Co-Founder \& Developer}{Laiter — software studio}{2017 -- 2019}{Mexico}
\begin{tight}
  \item Co-founded the studio; built client web applications end to end (Django, JavaScript) and the early usage-analytics dashboards customers ran decisions on; owned deployments and production support.
\end{tight}

\section*{Education}
\role{MSc Data Science}{London School of Economics (LSE)}{2026 -- 2027}{In progress, London}
\vspace{2pt}
\role{B.S. Computer Science \& Technology}{Tecnológico de Monterrey (ITESM)}{2016 -- 2021}{Avg 90/100}
\vspace{1pt}
{\color{soft}\small Semester abroad at RMIT University, Melbourne (Avg 94/100). IBM Data Science Professional Certificate (in progress).}

\section*{Technical Skills}
\skill{Backend}{Python, FastAPI, Django, GraphQL, Celery, PostgreSQL, Redis, RabbitMQ}
\skill{Frontend}{TypeScript, React, Next.js, JavaScript}
\skill{Payments \& Infra}{Stripe Connect, Docker, GitHub Actions, Grafana, S3}
\skill{AI / LLM}{LLM integration (Gemini), structured output; agent-orchestrated development (Claude Code, git worktrees)}
\skill{Data Science}{pandas, NumPy, scikit-learn, PyMC}
\skill{Languages spoken}{Spanish (Native), English (C2), German (A2), Italian (A1)}

\end{document}
